Online learning methods for financial time series forecasting

### 2017-11-12 slides/defense-slides.tex
New template and motivation slides

%\documentclass[xcolor=dvipsnames]{beamer}
\documentclass[compress,red]{beamer}
\mode<presentation>
%\usepackage[spanish,activeacute]{babel}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{adjustbox}
\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{multicol}
\usepackage{hhline}
\usepackage{pgf}
\usepackage{algorithm} 
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\def\R{{\mathbb R }}
\def\N{{\mathbb N }}
\usetheme{Warsaw}
% other themes: AnnArbor, Antibes, Bergen, Berkeley, Berlin, Boadilla, boxes, CambridgeUS, Copenhagen, Darmstadt, default, Dresden, Frankfurt, Goettingen,
% Hannover, Ilmenau, JuanLesPins, Luebeck, Madrid, Maloe, Marburg, Montpellier, PaloAlto, Pittsburg, Rochester, Singapore, Szeged, classic
%\usecolortheme{lily}
% color themes: albatross, beaver, beetle, crane, default, dolphin, dov, fly, lily, orchid, rose, seagull, seahorse, sidebartab, structure, whale, wolverine

@@

\useoutertheme[subsection=false]{smoothbars}

\setbeamertemplate{blocks}[rounded][shadow=true]

\author[P. Arce et al.]{Paola
Arce\inst{1}\and Jonathan Antognini\inst{1}\and Werner Kristjanpoller
\inst{2}\and Luis Salinas\inst{1,3}}

\institute[UTFSM]{
\inst{1} Departamento de Inform\'atica, UTFSM, Chile \\
\inst{2} Departamento de Industrias, UTFSM, Chile \\
\inst{3} CCTVal, UTFSM, Chile
}

\date[ISCEF 2016]{4th International Symposium in Computational Economics and Finance 2016}
\title[Cointegration model
for forecasting HF financial time series]{\Large Fast and adaptive cointegration based model for forecasting high frequency financial time series}

%\titlegraphic{
%   \includegraphics[width=1cm]{img/logo_DI}\hspace*{2.5cm}~%
%   \includegraphics[width=1.5cm]{img/logo_UTFSM}\hspace*{2.5cm}~%
%   \includegraphics[width=1cm]{img/logo_IND}
%}

@@

\section{Introduction}
\subsection{Motivation}

\begin{frame}
\frametitle{Motivation}
Most financial time series are non-stationary in nature. This implies that the statistical properties, such as mean and variance of the data change over time.
\end{frame}

>>>>

\documentclass{beamer}
\usetheme{metropolis}
%\usepackage[spanish,activeacute]{babel}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{adjustbox}
\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{multicol}
\usepackage{hhline}
\usepackage{pgf}
\usepackage{algorithm} 
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\def\R{{\mathbb R }}
\def\N{{\mathbb N }}

@@

\author{Paola Arce \\ Departamento de Inform\'atica, UTFSM \\ Thesis advisor: Luis Salinas}
\date{December 15, 2017}
\title{Online learning methods for financial time series forecasting}
\subtitle{PhD Thesis Defense}

\titlegraphic{
    \tikz[overlay,remember picture]
        \node[at=(current page.south east), anchor=south east] {
            \includegraphics[height=1.5cm]{img/DIT}
        };
}

@@

\section{Introduction}

\begin{frame}
\frametitle{Motivation}
Most financial time series are non-stationary in nature. This implies that the statistical properties, such as mean and variance of the data change over time. Therefore, financial time series forecasting is still a challenge.
\begin{figure}
\includegraphics[width=0.4\paperwidth]{img/forecast}
\end{figure}

\end{frame}
